formula1_allyears

### 2020-08-28 inst/formula1_allyears.Rmd
consistent use of years

Here I analyse Formula 1 results 2010-2019 using Plackett-Luce
likelihoods as implemented in the `hyper2` package.  Files like
`formula1_2017.txt` are directly copied from Wikipedia (with slight
whitespace changes).

```{r,label=f1yearsseparate,cache=TRUE}
f <- function(M){M[,-ncol(M)]} # removes 'points' column
o <- function(k){ordertable2supp(f(read.table(k)))}
F1_2010 <- o("formula1_2010.txt")
F1_2011 <- o("formula1_2011.txt")
F1_2012 <- o("formula1_2012.txt")
F1_2013 <- o("formula1_2013.txt")
F1_2014 <- o("formula1_2014.txt")
F1_2015 <- o("formula1_2015.txt")
F1_2016 <- o("formula1_2016.txt")
F1_2017 <- o("formula1_2017.txt")
F1_2018 <- o("formula1_2018.txt")
F1_2019 <- o("formula1_2019.txt")
```

```{r,label=combineallyears,cache=TRUE}
F1_list<- list(F1_2010, F1_2011, F1_2012, F1_2013, F1_2014, F1_2015, F1_2016, F1_2017, F1_2018, F1_2019)
F1_total <- F1_2010 + F1_2011 + F1_2012 + F1_2013 + F1_2014 + F1_2015 + F1_2016 + F1_2017 + F1_2018 + F1_2019
```

```{r,calculatemaxlikelhood,cache=TRUE}
m <- maxp(F1_total)
pie(m)
dotchart(m,pch=16,main='Formula 1, 2012-9')
```

```{r,workwithM}
M <- matrix(NA,length(pnames(F1_total)),2019-2010+1)
rownames(M) <- pnames(F1_total)
colnames(M) <- paste("y",10:19,sep="")

@@

image(x=2010:2019,y=seq_along(pnames(F1_total)),t(M))
```

@@

```{r,definefreqrace}
freqracers <- function(minraces){
(
	select(f(read.table("formula1_2010.txt")),minraces) + 
	select(f(read.table("formula1_2011.txt")),minraces) + 
	select(f(read.table("formula1_2012.txt")),minraces) + 
	select(f(read.table("formula1_2013.txt")),minraces) + 
	select(f(read.table("formula1_2014.txt")),minraces) + 
	select(f(read.table("formula1_2015.txt")),minraces) + 
	select(f(read.table("formula1_2016.txt")),minraces) + 
	select(f(read.table("formula1_2017.txt")),minraces) + 
	select(f(read.table("formula1_2018.txt")),minraces) 
	)
}

>>>>

Here I analyse Formula 1 results in a range of years using
Plackett-Luce likelihoods as implemented in the `hyper2` package.
Files like `formula1_2017.txt` are directly copied from Wikipedia
(with slight whitespace changes).

```{r}
years <- 2001:2015
```

```{r,label=f1yearsseparate,cache=TRUE}
f <- function(M){M[,-ncol(M)]} # removes 'points' column
o <- function(k){ordertable2supp(f(read.table(k)))}
filenamemaker <- function(year){paste("formula1_",year,".txt", sep="")}
F1_list <- list()
for(year in years){
	filename <- filenamemaker(year)
	jj <- paste("y",year,sep="")
	F1_list[[jj]] <- o(filename)
}
```

```{r,label=combineallyears,cache=TRUE}
F1_total <- hyper2()
for(i in F1_list){F1_total <- F1_total + i}
```

```{r,calculatemaxlikelhood,cache=TRUE}
m <- maxp(F1_total)
pie(m)
dotchart(m,pch=16,main=paste("Formula 1, years ",min(years)," to ",max(years)))
```

```{r,workwithM}
M <- matrix(NA,nrow=length(pnames(F1_total)),ncol=length(years))
rownames(M) <- pnames(F1_total)
colnames(M) <- paste("y",years,sep="")

@@

image(x=years,y=seq_along(pnames(F1_total)),t(M))
```

@@

```{r,definefreqrace}
freqracers <- function(minraces){ # minimum number of seasons
	out <- hyper2()
	for(year in years){
		out <- out + select(f(read.table(filenamemaker(year),minraces)))
	}	
	return(out)
}
